\documentclass{antiquebook}

\usepackage{macros}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{url}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage[outline]{contour}
\usepackage{tikz}
\usepackage{pifont}
\usepackage{fontspec}

\begin{document}
    \frontmatter
    \titleP

    \mainmatter
    \pagestyle{fancy}

    \chapter{Heavy is the Hand}

    \indent “Because I trust you.” \\

\indent He reaches for the knife. A cool breeze seeps in through the window, bending the trees in its path. 
Leaves whisper as they rustle along the bedroom wall, peering into the dark room. He takes your hand and opens it slowly. 
Your eyes meet as your fingers close around the handle. \\

\texttt{BEGIN Choice 1: Look away? (Y/N)} \\ 

\texttt{Choice 1 - YES} \\
\indent His gaze is deep, reaching, yearning, longing, and beneath it all, a fire crackles like chattering teeth. 
Click-clack, snip-crack, “Hurt me!” plead the teeth, “HURT ME!” they gargle as the gums burst and gush with blood. 
Wishes of deliverance flow red into the void. More blood splatters as the mouth begs in bouts of coughs. 
“Please\dots ” wheeze the teeth. You shudder, and the room burns back into frame, the chatter softens into the dry whooshing of rustling leaves. 
His hand closes around your fist, your fist clenches the handle, the handle brandishes the blade. 
Your eyes meet once again, but he does not pull you in. He does not absorb you into the enfleurage oils of his soul, 
seeking judgement's absolute; he does not lock you in the nullspace beneath gaze and above thought\dots 
That whole dimension is veiled now. His pupil trembles, his iris glows. The void spills and streams along his cheek; 
it trickles down and around his cheekbones, and along the corner of his mouth upon which appears a smile. “Do it,” he nods. \\


\texttt{Choice 1 - NO} \\
\indent You turn away and close your eyes. Everything disappears. In the distance, haloes of red and white make their way down Second Avenue. 
The hum of traffic and chatter fade in. You look to your right. Streaks of yellow and white, like violent starburst, charge toward you. 
One after the other they leave you with Döppler's echo and a lingering gust of wind. 
Your light turns green and your dark brown hair falls back down upon your shoulders. “Come on,” he says, “I have to catch this one.” 
Your hand, in his, leads you across the white-striped crossing. He doesn't look back. \\
You open your eyes again. \\

\texttt{END Choice 1} \\

\indent The blade gleams in the cold neon of the street lamps below. Foliage dances like black flames on the peeling wallpaper. 
Light clasps around him, drawing a white aura around his arms and jaw. He sits on the bed where the pillows lay a moment ago, 
facing the wall, his breath burdened but steady\dots The bedsheets crease and furrow as you kneel behind him. 
You steady yourself, placing your hand on his rugged shoulders. His grin warps his face so as to transpire from behind. 
Heavy is the hand which bears the blade.


\end{document}